Subjective Experience of Demands and Resources across O*NET Job Elements

### 2024-02-27 Submission.Rmd
tinkering
Revising introduction to challenge-hindrance framework - beginning

Research on the job demands-resources model [@demerouti2001job] and later job demands-resources theory [@bakker2017job] highlights the importance of work characteristics on the experience of motivation and strain as well as other, more distal outcomes. However, much of our existing knowledge regarding the way these relationships function is grounded in the assumption that certain job characteristics can generally be considered to be (positive) resources while others can be considered demands. We build on the work of a small, but growing number of researchers who argue that the work elements may be appraised simultaneously as resources and demands [@webster2011extending] or that appraisals may change over time [@rosen2020challenges], with primary aims of exploring 1) whether there is variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands, and 2) whether or not there is a match between the literature-implicated resources/demands and subjective ratings of these characteristics. Prior to presenting the current study in detail, we provide a brief overview of the relevant theories and relevant empirical work on this topic.

## The Job demands-Resources Theory

@@

## The Essential Role of Appraisal

@@

Demand --> appraisal (as challenge or hindrance)

Demand=Stressor

Decision (can overcome or not )

@@

## ARGUE FOR H1 and H2 (Are perceptions universal?)

@@

## Current Study and Hypotheses

>>>>

We build on the work of a small, but growing number of researchers who argue that the work elements may be appraised simultaneously as resources and demands [@webster2011extending] or that appraisals may change over time [@rosen2020challenges], with primary aims of exploring 1) whether there is variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands, and 2) whether or not there is a match between the literature-implicated resources/demands and subjective ratings of these characteristics. Prior to presenting the current study in detail, we provide a brief overview of the relevant theories and relevant empirical work on this topic.

@@

@@

@@

## Are Perceptions of Job Resources, Challenge Demands, and Hindrance Demands Universal?

@@
